A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-14 latex/main.tex
Updates from Overleaf

\begin{figure}
\centering
\includegraphics[width=\linewidth]{samples-per-day}
\caption{
TODO caption
}\label{fig:samples_per_day}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{inference-resources}
\caption{
TODO caption
}
\label{fig:inference_resources}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{samples-per-day}
\caption{
Daily statistics of samples analyzed
during the ARG inference process.
(A) The number of samples
processed from the input sequence alignments,
exactly matched to a node in the current ARG, and
added to the ARG
all peak in December, 2022
and subsequently around February, 2022.
(B) The fraction of exactly matched samples and
the fraction of samples added to the ARG
mirror each other.
Around the peak of sample volume,
the fraction of exactly matched samples
is relatively high (above 0.50).
As expected, this fraction later decreases
when sampling effort decreases.
(C) The mean HMM cost per sample is relatively high
at the beginning as the ARG had not accumulated
enough genetic diversity yet.
(D) Proportion of samples classified
by Scorpio designation.
These proportions reflect waves of infections
driven by the emergence of Alpha, Delta, and Omicron.
}\label{fig:samples_per_day}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{inference-resources}
\caption{
Usage of computational resources
during the ARG inference process.
(A) The amount of time to process a daily batch of samples
peaks when the sample volume is the highest.
(B) Mean time to process a sample remained low.
(C) Max RAM usage also peaks around the time
that sampling effort is the highest.
}
\label{fig:inference_resources}
\end{figure}
